%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {System Engineer (Security)} % Job title
    {Centene Corporation} % Organization
    {Rancho Cordova, California} % Location
    {Jan. 2020 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Leading efforts to automate workflows via python and REST API integrations.}
        \item {Configuration of static and dynamic web application scans.}
	\item {Management of Tenable.SC vulnerability scans for coverage across the entierprise.}
        \item {Administration of multiple threat and vulnerability management tools including Tenable.SC, Tenable.IO, Anomali, Recorded Future, Veracode, CloudGuard, Now Secure, and BitSight.}
      \end{cvitems}
    }



%---------------------------------------------------------
  \cventry
    {Engineering Director} % Job title
    {Capitol Compliance Management} % Organization
    {Sacramento, California} % Location
    {Jul. 2015 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architecture and oversight of Development and IT systems.}
        \item {Authoring and implementing best practices for security and devops processes.}
        \item {Full stack stack software engineering, developing bespoke applications and integrating various tools via REST APIs.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Senior Web Developer} % Job title
    {Prestwood I.T. Solutions} % Organization
    {Citrus Heights, California} % Location
    {Aug. 2014 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Back End Development in PHP, MySQL, VB, C\#, and MSSQL.}
        \item {Front End Development in HTML5/CSS3, JavaScript (jQuery, VueJS). }
        \item {Authored Standard Operating Procedures for Web Division.}
        \item {Technical Lead of Web Division.}
        \item {Served on Prestwood's Board of Directors.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Consultant} % Job title
    {Orcuttbay.com} % Organization
    {Santa Maria, California} % Location
    {May. 2009 - Jan. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Full Stack Web development utilizing Code Igniter Framework and WordPress CMS.}
        \item {Ubuntu Linux Apache2 server administration for multiple clients in shared environment, hosted onsite. }
        \item {Organic SEO campaigns with Google Analytics and Webmasters toolkits.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {30th Space Wing Public Affairs GS3} % Job title
    {United States Air Force} % Organization
    {Vandenberg Air Force Base, California} % Location
    {Oct. 2008 - Sept. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained and expanded 30th Space Wing Intranet site for Public Affairs.}
        \item {Developed and maintained Java Applet for emergency exercise communication.}
        \item {Acted as first point of contact between Vandenberg Air Force Base and the general public.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Webmaster} % Job title
    {El Dorado Broadcasting (formerly Clear Channel Radio)} % Organization
    {Santa Maria, California} % Location
    {Oct. 2006 - July. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained PHP/MySQL sites for all radio stations under El Dorado Broadcasters in Santa Maria market.}
      \end{cvitems}
    }



%---------------------------------------------------------
\end{cventries}
